% Chapter Template

\chapter{Literature Survey} % Main chapter title

\label{Chapter2} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

\lhead{Chapter 2. \emph{Literature Survey}} % Change X to a consecutive number; this is for the header on each page - perhaps a shortened title

Some of the papers studied for references are:
\begin{enumerate}
\item ``Mahnob-HCI-Tagging Database \emph{(Lichtenauer et. al., 2012)}''\cite{mahnobDataset}
\item ``Analysis of EEG signals and facial expressions for continuous emotion detection \emph{(Soleymani et. al., 2015)}''\cite{mahnobEmo}
\item ``Emotion Classification in Arousal Valence Model using MAHNOB-HCI Database \emph{(Wiem et. al., 2017)}''\cite{wiem}
\item ``Selection of the Most Relevant Physiological Features for Classifying Emotion \emph{(Godin et. al., 2015)}''\cite{sel}
\item ``Investigation of window size in classification of EEG-emotion signal with wavelet entropy and support vector machine \emph{(H. {Candra} et. al., 2015)}''\cite{window}

After reading these past journals, conference papers and theses, I arrived to these conclusions:
\begin{enumerate}
    \item Human Computer Interaction is a complex topic, and it requires Medical, Mathematical (Signal Processing and Statistical) Knowledge.
    \item There is no way to remove noise and artefacts from collected signal once it has been collected. Hence, while collecting data, you need to be as accurate and careful as possible.
    \item Multiple organs interfere with brain signals and hence are a source of noise to the EEG signals. Subtracting or negating the noise provided by these organs is not always possible, and if possible, it isn't quite precise. Some examples are 
    \begin{enumerate}
        \item Heart activities or ECG signals
        \item Eye Activity, i.e., rotation and focus of the eyes.
        \item Loss of focus or attention by the participant. In this case, the brain activities are not a result of the desired external stimuli , but by wither some internal stimuli or other undesired external stimuli.
    \end{enumerate}
    \item There aren't many clean datasets available freely.
    \item Most of the experiments were conducted on only the arousal and valence scales. The control and prediction scales were mostly unused in the experiment or were simply not provided in the dataset that the researchers used.
    \item The accuracy varies a lot according to the methodology and dataset used.
    \item Given the brain activity reading, we can segment it into chunks of data of smaller durations, and use the label (ground truth values) on the parent data as the label of all the chunks.\cite{window}
\end{enumerate}
\end{enumerate}
